---
title: "Causality and Program evalustion_Assignment"
author: 'Sunyoung Ji, ID: 229979 (TU Dortmund)'
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Used libraries are given below:
```{r library, include=FALSE}
library(tidyverse)
library(dplyr)
library(readr)
library(rdd)
library(rddtools)
```

# 0. Set up

```{r set up, echo=TRUE, warning=FALSE}
ebike <- read_csv("dataset1.csv")
ebike <- as_tibble(ebike)
view(ebike)
```

# 1. Task(a)

```{r task(a), echo=TRUE}
threshold <- ggplot(ebike,
                    aes(x = distance, y = free_bicycle)) +
  geom_point() +
  labs(x = "Distance", y = "Free bicycle",
       title = ("The compliance with the 5km rule")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = 5, colour = "red",
             size = 1, linetype = "dashed") +
  annotate("text", x = 4, y = 1, label = "5km",
           size=4, color = "red")
threshold
```
This graph illustrates that "dataset1" satisfies the rule of distance.

# Task(b)

From (a), we can see that the treatment(`free_bicycle`) is assigned by the threshold(5km Rule). Therefore, the impact of free ebike policy can be estimated by Sharp Regression Discontinuity Designs. It should hold the following assumptions:
1) There is a discontinuity in the probability of treatment at the threshold
2) Individuals’ value of the treatment variable was not manipulated
3) Continuity of potential outcomes around threshold

# Task(c)

McCrary Sorting Test:
We can check that the score would not manipulated in the McCrary test. The density of distance almost continuous.

```{r manipulation test, echo = TRUE}

DCdensity(ebike$distance, cutpoint = 5, ext.out = FALSE, plot = TRUE)

```

# Task (d)
 
Placebo test with age and number of roommates as dependent variables:

```{r placebo, echo=TRUE}

plac_age <-lm(age ~ distance, data = ebike)
plac_room <-lm(number_roomates ~ distance, data = ebike)

plac_linear <- cbind(plac_age$coefficients[2], plac_room$coefficients[2])
colnames(plac_linear) <- c("age", "roommates")
rownames(plac_linear) <- "plac_linear"

plac_linear <- round(plac_linear, 4)

```

Through the placebo regression, we can know that these dependent variables have almost zero linear dependency with other variables. 

However, when these dependent variables are applied for the same model in (e), the placebo effects increase:

```{r plac rd, echo=TRUE}
plac_age_rd <- rdd_data(y = ebike$age, x = ebike$distance,
                     cutpoint = 5)
reg_para_age <- rdd_reg_lm(rdd_object=plac_age_rd)

plac_room_rd <- rdd_data(y = ebike$number_roomates, x = ebike$distance,
                     cutpoint = 5)
reg_para_room <- rdd_reg_lm(rdd_object=plac_room_rd)

plac_rd <- cbind(reg_para_age$coefficients, reg_para_room$coefficients)
colnames(plac_rd) <- c("age", "roommates")
plac_rd <- round(plac_rd[2,], 4)
```

We can comparison two results from two models:
```{r plac comparison, echo=TRUE}
rbind(plac_linear, plac_rd)
```

# Task (e)

```{r obs hist, echo = TRUE}

distance_hist <- ggplot(ebike, aes(distance)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Distance", y = "Count",
       title = ("Histogram of Distance")) +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(xintercept = 5, colour = "red",
             size = 1, linetype = "dashed") +

  annotate("text", x = 4, y = 1000, label = "5km",
           size=4, color = "red")

distance_hist
```

As histogram of distance shows, we have observations that are distributed very differently depending on the distance. Including more observations farther away from threshold would generate excessive bias. Thus, I choose a local linear regression model and bandwidth 1.

1) The RDD model:
$$
Y=\alpha + \tau*D + \beta_1(X-c) + \beta_2*D(X-c) + \epsilon
$$

2) Finding a bandwidth: Kernel selection:

```{r band, echo=TRUE}

rdd_data <- rdd_data(y = ebike$score, x = ebike$distance,
                     cutpoint = 5)

bandwidth <- rdd_bw_cct_estim(rdd_data)
bandwidth

```

3) RD simulation: 
```{r rd sim, echo=TRUE}

reg_para_bw1 <- rdd_reg_lm(rdd_object=rdd_data, bw = 1)
reg_para_bw1

ebike %>%
  select(distance, score) %>%
  mutate(threshold = as.factor(ifelse(distance >= 5, 1, 0))) %>%
  ggplot(aes(x = distance, y = score, color = threshold)) +
  geom_point(size = 0.3) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = "none") +
  geom_vline(xintercept = 5, color = "black",
             size = 1, linetype = "dashed") +
  labs(y = "Exam Score",
       x = "Distance")
```

# Task(f)

According to result from McCrary test, the external validity of the model in (e) is satisfied.

```{r rd mc, echo=TRUE}

DCdensity(rdd_data$x, cutpoint = 5, ext.out = FALSE, plot = TRUE, bw = 1)

```